%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

% ATS-friendly PDF text extraction (T1 + Latin Modern)
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\PassOptionsToPackage{hyphens}{url}
\usepackage[hidelinks,breaklinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\input{glyphtounicode}

\hypersetup{
  pdftitle={Eleni Zafeiri Resume},
  pdfauthor={Eleni Zafeiri},
  pdfsubject={Resume},
  pdfkeywords={Software Engineer, Full Stack Developer, React, Node.js, JavaScript, REST API, Git, Agile, Remote, CS}
}
\makeatletter
\g@addto@macro\UrlBreaks{\do\/}
\makeatother

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\large\bfseries
}{}{0em}{}[\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeadingLink}[4]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small \href{#1}{\textbf{\underline{#2}}} $|$ \emph{#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{\textbullet}
\renewcommand\labelitemii{\textbullet}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeExperienceHeading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}\ | \textit{\small #2} & \textit{\small #3} \\
    \end{tabular*}\vspace{-7pt}
}

% GitHub URLs
\newcommand{\githubhookgrab}{https://github.com/feirw/hook-and-grab}
\newcommand{\githubcsplatform}{https://technotesgr.com}
\newcommand{\githubathensgo}{https://github.com/feirw/athensgoo}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\LARGE\bfseries Eleni Zafeiri} \\ \vspace{1pt}
    {\small\textit{Software Engineer · B.S.\ Computer Science}} \\ \vspace{2pt}
    \small
    \href{https://github.com/feirw}{github.com/feirw} \quad
    Athens, Greece (Open to Remote) \quad
    \href{tel:+306983426662}{+30 698 342 6662} \quad
    \href{mailto:elenzaff@icloud.com}{elenzaff@icloud.com} \quad
    \href{https://www.linkedin.com/in/elenizafeiri}{linkedin.com/in/elenizafeiri} \quad
    \href{https://elenizafeiri.com/}{elenizafeiri.com}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National and Kapodistrian University of Athens}{Athens, Greece}
      {Bachelor of Science in Computer Science, GPA: 8.54/10}{Expected Jun. 2028}
      \resumeItemListStart
        \resumeItem{Coursework: Data Structures \& Algorithms, OOP, Operating Systems, Databases, Computer Networks, Software Engineering.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeExperienceHeading{Software Engineer}{HongLong, Remote}{Sep. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Develop and maintain WordPress-based web products end-to-end, writing HTML/CSS/JS and shipping weekly releases across multiple codebases.}
        \resumeItem{Reduced production defects by 40\% in six months through systematic root-cause analysis and pre-release regression testing.}
        \resumeItem{Resolve 7+ support tickets per week, independently triaging by severity in a fully remote, async environment.}
        \resumeItem{Collaborate with designers and stakeholders via Slack and GitHub to translate requirements into technical specs.}
      \resumeItemListEnd

    \resumeExperienceHeading{Technical Project Manager Intern}{Threenitas, Hybrid}{Sep. 2025 -- Oct. 2025}
      \resumeItemListStart
        \resumeItem{Facilitated Scrum ceremonies for engineering teams of 5+, tracking dependencies and ensuring on-time releases.}
        \resumeItem{Authored technical specs and acceptance criteria that reduced rework cycles and improved cross-team alignment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Engineering Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeadingLink
          {\githubcsplatform}
          {TechnotesGR --- Learning Platform}
          {React.js, TypeScript, Tailwind CSS}
          {Jun. 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Designed, built, and deployed a production learning platform with quizzes, spaced-repetition flashcards, and algorithm visualizations at \href{https://technotesgr.com}{technotesgr.com}.}
            \resumeItem{Improved usability through iterative user testing, reducing task-completion time and increasing session duration.}
            \resumeItem{Manage the full deployment pipeline and ship ongoing feature releases with Git-based version control.}
          \resumeItemListEnd
      \resumeProjectHeadingLink
          {https://github.com/feirw}
          {Epirus Shield --- Scam Detection App}
          {Mobile App, AI, Real-Time Audio Processing}
          {May 2026}
          \resumeItemListStart
            \resumeItem{Built a real-time scam detection system that flags fraudulent callers during phone calls, developed for the Bank of Epirus.}
            \resumeItem{Integrated AI-driven audio analysis to detect suspicious patterns and alert users in real time.}
            \resumeItem{\textbf{1st place} out of 45 competing entries.}
          \resumeItemListEnd
      \resumeProjectHeadingLink
          {\githubhookgrab}
          {Hook \& Grab --- Full-Stack Marketplace}
          {JavaScript, CSS, HTML, Tailwind CSS}
          {Nov. 2024 -- Dec. 2024}
          \resumeItemListStart
            \resumeItem{Built a full-stack marketplace with REST endpoints for listings, auth, and transactions.}
            \resumeItem{\textbf{1st place} out of 10+ teams at a university hackathon.}
          \resumeItemListEnd
      \resumeProjectHeadingLink
          {\githubathensgo}
          {AthensGo --- AI Itinerary Generator}
          {Mobile App, AI Integration}
          {Nov. 2025}
          \resumeItemListStart
            \resumeItem{Scoped MVP features for an AI-powered itinerary app targeting three user personas with accessibility constraints.}
            \resumeItem{Designed user flows and wireframes for the core booking experience.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript (ES6+), TypeScript, HTML5, CSS3, Java, C, C++} \\
     \textbf{Frontend}{: React.js, Tailwind CSS, responsive design, component-based architecture} \\
     \textbf{Backend}{: Node.js, REST APIs, WordPress (themes, plugins, PHP hooks)} \\
     \textbf{Tools \& Platforms}{: Git, GitHub, VS Code, npm, Agile/Scrum, CI/CD workflows} \\
     \textbf{Soft Skills}{: Async remote collaboration, clear written communication, ownership, fast learning, cross-functional teamwork, adaptability} \\
    }}
 \end{itemize}


%-----------VOLUNTEER EXPERIENCE-----------
\section{Volunteer Experience}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Project Manager}{: DiT Coding Club---organized 4+ hackathons (150+ participants) \hfill \textit{Dec. 2024 -- Present}} \\
     \textbf{Tech Mentor}{: Sistech Global---trained refugee women entering tech \hfill \textit{Sep. 2025 -- Dec. 2025}} \\
     \textbf{Volunteer Coordinator}{: WELEAD---coordinated logistics and workshops for 3+ tech events (100+ participants) \hfill \textit{Mar. 2025 -- Aug. 2025}} \\
     \textbf{Hackathon Coordinator}{: Texas A\&M $\times$ UoA international event (80+ participants) \hfill \textit{Feb. 2025 -- Mar. 2025}} \\
    }}
 \end{itemize}


%-----------CERTIFICATIONS & LANGUAGES-----------
\section{Certifications \& Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Certifications}{: Prompt Engineering (AWS) $|$ Project Management (Workearly) $|$ Data Storytelling (Deloitte) $|$ Digital Literacy (Cisco)} \\
     \textbf{Languages}{: English (C2---ECPE, LRN) $|$ Greek (native) $|$ French (B2---DELF)} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
